### 2004-07-08 Documentation/part1.tex
*** empty log message ***

\section{Units in \GLOBES\ and the integrated luminosity}

@@

\GLOBES\ can compute the probabilities in vacuum
with the following function:
\begin{function}
\GLBNS{glbVacuumProbability}
{\tt double glbVacuumProbability(int l, int m, int panti,double E, double L)} returns the neutrino oscillation probability $\nu_l \rightarrow \nu_m$ for the energy {\tt E} and the baseline {\tt L} in vacuum. The parameter
{\tt panti} is $+1$ for neutrinos and $-1$ for antineutrinos. 
\end{function}
In addition, the oscillation probabilities in matter can be obtained
with:
\begin{function}
\GLBNS{glbProfileProbability}
{\tt double glbProfileProbability(int l, int m, int panti,double E)}
 returns the neutrino oscillation probability $\nu_l \rightarrow \nu_m$ for the energy {\tt E} in matter. The parameter
{\tt panti} is $+1$ for neutrinos and $-1$ for antineutrinos.
The matter density profile including baseline is the one from the last
evaluated experiment. 
\end{function}
THIS FUNCTION MAY OBTAIN AN EXPERIMENT INDEX (WW).
\section{Event rates}
\index{Event rates}
One can also return event rates in \GLOBES , but this feature
requires some knowledge about the experiment definition. \GLOBES\
currently supports rule-based and channel-based event rate functions,
where the information is in most cases written into a file.
The rule-based functions are:
\begin{function}
\GLBNS{glbShowRuleRates}
{\tt int glbShowRuleRates(FILE* stream, int exp, int rule, int pos,
int effi, int bgi, int coeffi, int signal)} prints the binned rule rates as
list with energy and event rate to the file {\tt stream} (either an
open file, or {\tt stdout}). A specific experiment {\tt exp} and a 
specific rule {\tt rule} have to be chosen, as well as the signal
or background rate {\tt signal} (either \GLB{GLB\_SIG} or \GLB{GLB\_BG}).
The position {\tt pos} refers to the component within the signal or 
background, and can also be {\tt GLB\_ALL}. The function may return
the rates with (\GLB{GLB\_W\_COEFF}) or without (\GLB{GLB\_WO\_COEFF})
overall efficieny coefficient, as it is specified by {\tt coeffi}. 
In addition, it may contain the post-smearing efficiencies (set
{\tt effi} to \GLB{GLB\_W\_EFF} or \GLB{GLB\_WO\_EFF}), and the
post-smearing backgrounds (set
{\tt bgi} to \GLB{GLB\_W\_BG} or \GLB{GLB\_WO\_BG}). The pre-smearing
efficiencies and backgrounds cannot be accessed at the rule level.
The return value
is $0$ if successful, and $-1$ if unsuccessful.
\end{function}
\begin{function}
\GLBNS{glbShowTotalRuleRates}
{\tt double glbShowTotalRuleRates(int exp, int rule, int pos,
int effi, int bgi, int coeffi, int signal)} returns the total rates with
the same parameters as {\tt glbShowRuleRates}.
\end{function}
(THIS SYNTAX NEEDS TO BE CHECKED, BECAUSE FUNCTION IS NOT YET IMPLEMENTED - WW)

The function {\tt glbShowTotalRuleRates} is especially useful if
one wants to draw bi-rate graphs with total event rates, or look
for the $(\deltacp,\theta_{13})$-degeneracy by the intersection of 
neutrino and antineutrino constant event rate curves.

In addition, \GLOBES\ has a channel-based rate function:
\begin{function}
\GLBNS{glbShowChannelRates}
{\tt int glbShowChannelRates(FILE *stream,
int exp, int channel, int smearing, int effi, int bgi)}
prints the binned channel rates as
list with energy and event rate to the file {\tt stream} (either an
open file, or {\tt stdout}). A specific experiment {\tt exp} and a 
specific channel {\tt channel} have to be chosen.
The function may return
the rates before (\GLB{GLB\_PRE}) or after (\GLB{GLB\_POST})
the energy smearing, as it is specified by {\tt smearing}.
In addition, it may contain the pre- and post-smearing efficiencies (set
{\tt effi} to \GLB{GLB\_W\_EFF} or \GLB{GLB\_WO\_EFF}), and the
pre- and post-smearing backgrounds (set
{\tt bgi} to \GLB{GLB\_W\_BG} or \GLB{GLB\_WO\_BG}). Note that
the post-smearing efficiencies and backgrounds cannot be taken into
account if the rates are returned before the energy smearing.
The return value
is $0$ if successful, and $-1$ if unsuccessful.
\end{function}

@@

\begin{function}
\GLBNS{glbXSection}
{\tt double glbXSection(int ident, double E, int l, int anti)} returns
the cross section of cross section number {\tt ident} for the flavor $\nu_l$ 
and polarity {\tt anti} ($+1$: neutrinos, $-1$: antineutinos) at the energy {\tt E}.
\end{function}
Note that all flux or flavor numbers run from $0$ to $N-1$ in these functions.

(THIS FUNCTION MAY GET AN EXPERIMENT INDEX IF NOT THROUGH-COUNTED IN AEDL!)

@@

\example{The impact of systematics, correlations, and degeneracies}{
\label{ex:corrproj}
\index{Bar charts}
\index{Systematics on/off}
Here it is demonstrated how one can successively include systematics, correlations, and degeneracies at the example of the $\stheta$-sensitivity limit.
An important part of this example is how two switch the systematics off,
\ie, how to obtain the sensitivity limit from statistics only. Since
this example is very advanced, we only show the respective function of the code:
\begin{quote}
{\tt 
/* Calculate chi2 with statistics only */ \\
double CalcNoSystematics(double theldm,double thex) \\
\{ \\
\hspace*{0.5cm} /* Switch systematics off for all exps and all rules */ \\
\hspace*{0.5cm} glbSwitchSystematics(GLB\_ALL,GLB\_ALL,GLB\_OFF); \\
\\
\hspace*{0.5cm} /* Calculate Chi2-list as if systematics were on */ \\
\hspace*{0.5cm} double res=CalcSystematics(theldm,thex); \\
\\
\hspace*{0.5cm} /* Switch systematics on for all exps and all rules */ \\
\hspace*{0.5cm} glbSwitchSystematics(GLB\_ALL,GLB\_ALL,GLB\_ON); \\
\\
\hspace*{0.5cm} return res; \\
\} \\
}
\end{quote}

@@

@@

>>>>

\section{Units in \GLOBES\ and the integrated luminosity}
\label{sec:luminosity}

@@

\GLOBES\ can compute the probabilities in vacuum
with the following function:
\begin{function}
\GLBNS{glbVacuumProbability}
{\tt double glbVacuumProbability(int l, int m, int panti,double E, double L)} returns the neutrino oscillation probability $\nu_l \rightarrow \nu_m$ for the energy {\tt E} and the baseline {\tt L} in vacuum. The parameter
{\tt panti} is $+1$ for neutrinos and $-1$ for antineutrinos. 
\end{function}
In addition, the oscillation probabilities in matter can be obtained
with:
\begin{function}
\GLBNS{glbProfileProbability}
{\tt double glbProfileProbability(int l, int m, int panti,double E)}
 returns the neutrino oscillation probability $\nu_l \rightarrow \nu_m$ for the energy {\tt E} in matter. The parameter
{\tt panti} is $+1$ for neutrinos and $-1$ for antineutrinos.
The matter density profile including baseline is the one from the last
evaluated experiment. 
\end{function}
THIS FUNCTION MAY OBTAIN AN EXPERIMENT INDEX (WW).
\section{Event rates}
\index{Event rates}
One can also return event rates in \GLOBES , but this feature
requires some knowledge about the experiment definition. 
In fact, many of these functions are very advanced, which means
that the reader who wants to use them should be familiar with
\Secs~\ref{sec:channel} and~\Sec~\ref{sec:rules} of the \AEDL\ manual.

\GLOBES\ currently supports rule-based and channel-based event rate functions, where the information is in written into a file
or returned in a list. The rule-based functions are:
\begin{function}
\GLBNS{glbShowRuleRates}
{\tt int glbShowRuleRates(FILE* stream, int exp, int rule, int pos,
int effi, int bgi, int coeffi, int signal)} prints the binned rule rates as
list with energy and event rate to the file {\tt stream} (either an
open file, or {\tt stdout}). A specific experiment {\tt exp} and a 
specific rule {\tt rule} have to be chosen, as well as the signal
or background rate {\tt signal} (either \GLB{GLB\_SIG} or \GLB{GLB\_BG}).
The position {\tt pos} refers to the component within the signal or 
background, and can also be {\tt GLB\_ALL}. The function may return
the rates with (\GLB{GLB\_W\_COEFF}) or without (\GLB{GLB\_WO\_COEFF})
overall efficieny coefficient, as it is specified by {\tt coeffi}. 
In addition, it may contain the post-smearing efficiencies (set
{\tt effi} to \GLB{GLB\_W\_EFF} or \GLB{GLB\_WO\_EFF}), and the
post-smearing backgrounds (set
{\tt bgi} to \GLB{GLB\_W\_BG} or \GLB{GLB\_WO\_BG}). The pre-smearing
efficiencies and backgrounds cannot be accessed at the rule level.
The return value
is $0$ if successful, and $-1$ if unsuccessful.
\end{function}
\begin{function}
\GLBNS{glbTotalRuleRate}
{\tt double glbTotalRuleRate(int exp, int rule, int pos,
int effi, int bgi, int coeffi, int signal)} returns the total rates with
the same parameters as {\tt glbShowRuleRates}.
\end{function}
The function {\tt glbTotalRuleRate} is especially useful if
one wants to draw bi-rate graphs with total event rates, or look
for the $(\deltacp,\theta_{13})$-degeneracy by the intersection of 
neutrino and antineutrino constant event rate curves.
%
In order to obtain information on the structure of the rules, 
a number of additional functions are provided:
\begin{function}
\GLBNS{glbGetNumberOfRules}
{\tt int glbGetNumberOfRules(int exp)} returns the number of
rules in experiment {\tt exp}.
\end{function}
\begin{function}
\GLBNS{glbGetLengthOfRule}
{\tt int glbGetLengthOfRule(int exp, int rule, int signal)} returns
the length of rule {\tt rule} in experiment {\tt exp}. The parameter
{\tt signal} can be either \GLB{GLB\_SIG} for the number of signal
components or \GLB{GLB\_BG} for the number of background components.
\end{function}
\begin{function}
\GLBNS{glbGetNormalizationInRule}
{\tt double glbGetNormalizationInRule(int exp, int rule, int signal)}
returns the normalization (normalization or background center)
in rule {\tt rule} of the experiment {\tt exp}.
The parameter {\tt signal} refers to signal (\GLB{GLB\_SIG}) or background
(\GLB{GLB\_BG}).
\end{function}
\begin{function}
\GLBNS{glbGetChannelInRule}
{\tt int glbGetChannelInRule(int exp, int rule, int pos, int signal)}
returns the channel number in rule {\tt rule} at the position {\tt pos}
of the experiment {\tt exp}.
The parameter {\tt signal} refers to signal (\GLB{GLB\_SIG}) or background
(\GLB{GLB\_BG}).
\end{function}
\begin{function}
\GLBNS{glbGetCoefficientInRule}
{\tt double glbGetCoefficientInRule(int exp, int rule, int pos, int signal)}
returns the coefficient of the component {\tt pos} in rule {\tt rule} 
of the experiment {\tt exp}.
The parameter {\tt signal} refers to signal (\GLB{GLB\_SIG}) or background
(\GLB{GLB\_BG}).
\end{function}

In addition, \GLOBES\ has channel-based rate functions:
\begin{function}
\GLBNS{glbShowChannelRates}
{\tt int glbShowChannelRates(FILE *stream,
int exp, int channel, int smearing, int effi, int bgi)}
prints the binned channel rates as
list with energy and event rate to the file {\tt stream} (either an
open file, or {\tt stdout}). A specific experiment {\tt exp} and a 
specific channel {\tt channel} have to be chosen.
The function may return
the rates before (\GLB{GLB\_PRE}) or after (\GLB{GLB\_POST})
the energy smearing, as it is specified by {\tt smearing}.
In addition, it may contain the pre- and post-smearing efficiencies (set
{\tt effi} to \GLB{GLB\_W\_EFF} or \GLB{GLB\_WO\_EFF}), and the
pre- and post-smearing backgrounds (set
{\tt bgi} to \GLB{GLB\_W\_BG} or \GLB{GLB\_WO\_BG}). Note that
the post-smearing efficiencies and backgrounds cannot be taken into
account if the rates are returned before the energy smearing.
The return value
is $0$ if successful, and $-1$ if unsuccessful.
\end{function}
\begin{function}
\GLBNS{glbGetChannelRates}
{\tt int glbGetChannelRates(double** data,
size\_t* length, int exp, int channel, int smearing)}
writes the binned raw channel rates to the list {\tt data}
and the length of this list to {\tt length}. 
A specific experiment {\tt exp} and a 
specific channel {\tt channel} have to be chosen.
The function may return
the rates before ({\tt smearing} is \GLB{GLB\_PRE}) or after ({\tt smearing} is \GLB{GLB\_POST})
the energy smearing, where no user-defined data
(pre-/post-smearing efficiencies or backgrounds) are taken into account.
The return value is $-1$ if unsuccessful.
\end{function}
\begin{function}
\GLBNS{glbGetUserData}
{\tt int glbGetUserData(double** data,
size\_t* length, int exp, int channel, int smearing, int bgeff)}
writes the binned user-defined backgrounds or efficiencies 
to the list {\tt data} and the length of this list to {\tt length}. 
A specific experiment {\tt exp} and a 
specific channel {\tt channel} have to be chosen.
The function may return
the pre- ({\tt smearing} is \GLB{GLB\_PRE}) or post- ({\tt smearing} is \GLB{GLB\_POST}) smearing backgrounds ({\tt bgeff} is \GLB{GLB\_BG}) 
or efficiencies ({\tt bgeff} is \GLB{GLB\_EFF}). 
The return value is $-1$ if unsuccessful.
\end{function}
Since \GLOBES\ reserved the memory for the lists returned in these
functions, which it allocates on an internal stack, one has to reset
the stack at the end of the rates access with
\begin{function}
\GLBNS{glbResetRateStack}
{\tt void glbResetRateStack()} resets the rate stack used for the
lists returned from {\tt glbGetChannelRates} or {\tt glbGetUserData}.
\end{function}
A code excerpt to show the channel rates may look like this:
\begin{quote}
{\tt
 double* rates; \\
  size\_t length; \\
  glbGetChannelRates(\&rates,\&length,0,0,GLB\_PRE); \\
  int i; \\
  for(i=0;i<length;i++) printf("\%g $\backslash$n",rates[i]); \\
  glbResetRateStack(); \\
}
\end{quote}
Finally, one can find the number of channels of an experiment:
\begin{function}
\GLBNS{glbGetNumberOfChannels}
{\tt int glbGetNumberOfChannels(int exp)} returns the number of 
channels of experiment {\tt exp}.
\end{function}

@@

\begin{function}
\GLBNS{glbXSection}
{\tt double glbXSection(int exp, 
int ident, double E, int l, int anti)} returns
the cross section of experiment {\tt exp}, 
cross section number {\tt ident} for the flavor $\nu_l$ and polarity {\tt anti} ($+1$: neutrinos, $-1$: antineutinos) at the energy {\tt E}.
\end{function}
Note that all flux or flavor numbers run from $0$ to $N-1$ in these functions.

@@

Many of the parameters in experiment definitions can be changed
at running time. For example, we have introduced in 
\Sec~\ref{sec:luminosity} possibilities to change the integrated
luminosity, which consists of source power, running time, and target mass.
In this chapter, we discuss more sophisticated
experiment changes. However, since \GLOBES\ computes a lot of
information only once when an experiment is loaded, many
parameters can not be changed at running time. For example,
the energy resolution function or the number of bins are used
to compute the smearing matrix already at the initialization
of the experiment, which saves a lot of computation
time for most applications. In \Sec~\ref{sec:aedlparams}, we 
introduce a mechanism how one can even change these \AEDL\ parameters
during running time.

\section{Baseline and matter density profile}

In order to change the baseline of an experiment, it is important
to keep in mind that each experiment has a profile type defined
in the \AEDL\ file (average density, PREM profile with a given
number of steps, or arbitrary profile). One can check the currently
used profile type with
\begin{function}
\GLBNS{glbGetProfileType}
{\tt int glbGetProfileType(int exp)} returns the matter density profile
type of experiment {\tt exp}.
\end{function}
For each profile type, one can easily change the baseline with {\tt glbSetBaselineInExperiment},
where the average density or the PREM profile are re-computed, or the
steps in the arbitrary profile are re-scaled. Of course, though this
function is sufficient in most cases, it does often not make sense
for arbitrary matter density profiles.
\begin{function}
\GLBNS{glbSetBaselineInExperiment}
{\tt int glbSetBaselineInExperiment(int exp, double baseline)}
sets the baseline length in experimente {\tt exp} to {\tt baseline}.
The function returns $-1$ if it was not successful.
\end{function}
Note that {\tt glbSetBaselineInExperiment} does not change the
profile type in the experiment. The counterpart of this function is:
\begin{function}
\GLBNS{glbGetBaselineInExperiment} 
{\tt double glbGetBaselineInExperiment(int exp)} returns the
baseline length currently used for experiment {\tt exp}.
\end{function}
One can not change the profile type of an experiment manually
during running time. However, one can change the matter density
profile, where the profile type is automatically changed to three
(arbitrary matter density profile). In addition, a number of functions 
are provided to compute possible matter density profiles (average density,
PREM profile). In general, a matter density profile in \GLOBES\ with
$N$ layers is represented by a list of lengths 
\begin{equation}
\mathrm{Lengths} = (x_1,x_2, \hdots, x_N) 
\end{equation}
and a list of densities
\begin{equation}
\mathrm{Densities} = (\rho_1,\rho_2, \hdots, \rho_N), 
\end{equation}
where the baseline is given by
\begin{equation}
L = \sum\limits_{i=1}^N x_i.
\end{equation}
In C, lists are represented as pointers to the first element:
\begin{quote}
{\tt  
  double* densities;
\end{quote}
Many of the \GLOBES\ baseline functions take and return
such lists as parameters, and are therefore more sophisticated
to handle. In general, any function
{\em returning} lists reserves the memory space for them.
It is then up to the user to return the allocated memory!
In addition, they normally return the length of the lists $N$
in form of a pointer, where the corresponding memory space 
has to be provided by the user (normally, it is enough to declare
a variable of the type {\tt size\_t} corrsponding to positive
integer numbers).
The following functions return matter density profiles:
\begin{function}
\GLBNS{glbLoadProfileData}
{\tt int glbLoadProfileData(const char* filename, size\_t *layers, double **lengths, double **densities)} loads a density file from the file
{\tt filename}. It returns the number of layers {\tt layers}, the
list of lengths {\tt lengths}, and the list of densities {\tt densities}.
\end{function}
The file should contain in each line a length and density for one layer,
which are separated by an empty space.
\begin{function}
\GLBNS{glbStaceyProfile}
{\tt int glbStaceyProfile(double baseline, size\_t layers, double **lengths, double **densities)} creates a PREM/Stacey matter density profile with a
number of {\tt layers} steps for the baseline {\tt baseline}. The list of lengths {\tt lengths} and the list of densities {\tt densities} are returned.
\end{function}
\begin{function}
\GLBNS{glbAverageDensityProfile}
{\tt glbAverageDensityProfile(double baseline, double **lengths, 
double **densities)} creates a average matter density profile from the PREM/Stacey profile with one step for the baseline {\tt baseline}. The list of lengths {\tt lengths} and the list of densities {\tt densities} are returned.
\end{function}
\begin{function}
\GLBNS{glbStaceyProfile}
{\tt int glbGetProfileDataInExperiment(int exp,size\_t *layers, double** lengths, double** densities)} returns the matter density profile 
currently used for experiment {\tt exp}. The number of layers {\tt layers}, the list of lengths {\tt lengths}, and the list of densities {\tt densities} are returned.
\end{function}
All these functions return $-1$ if they were not successful.

The counterpart of these functions to assign a specific matter density
profile to an experiment is
\begin{function}
\GLBNS{glbSetProfileDataInExperiment}
{\tt int glbSetProfileDataInExperiment(int exp, size\_t layers,const double* lengths, const double* densities)} sets the matter density of experiment
{\tt exp} to an arbitrary profile with {\tt layers} steps. The density
layers are specified by the lists {\tt lengths} and {\tt densities}.
The function returns $-1$ if it was not successful.
\end{function}
Note that this function requires that the memory space for the lists
be reserved already.

Finally, let us take a look at two examples. This example changes
the baseline length to $7\,500 \, \mathrm{km}$, where the average 
matter density is manually computed:
\begin{quote}
{\tt  
  double* lengths; \\
  double* densities; \\
  glbAverageDensityProfile(7500,\&lengths,\&densities); \\
  glbSetProfileDataInExperiment(0,1,lengths,densities); \\
  free(lengths); \\
  free(densities); \\
}
\end{quote}
In the second example, we change the baseline to a PREM profile with
$100$ matter density steps and print them:
\begin{quote}
{\tt
  double* lengths; \\
  double* densities; \\
  glbStaceyProfile(7500,100,\&lengths,\&densities); \\
  int i; \\
  for(i=0;i<100;i++) printf("\%g \%g $\backslash$n",lengths[i],densities[i]); \\
  glbSetProfileDataInExperiment(0,100,lengths,densities); \\
  free(lengths);\\
  free(densities);\\
}
\end{quote}

\example{The impact of systematics, correlations, and degeneracies}{
\label{ex:barcharts}
\index{Bar charts}
\index{Systematics on/off}
Here it is demonstrated how one can successively include systematics, correlations, and degeneracies at the example of the $\stheta$-sensitivity limit.
An important part of this example is how two switch the systematics off,
\ie, how to obtain the sensitivity limit from statistics only. Since
this example is very advanced, we only show the respective function of the code:
\begin{quote}
{\tt 
/* Calculate chi2 with statistics only */ \\
double CalcNoSystematics(double theldm,double thex) \\
\{ \\
\hspace*{0.5cm} /* Switch systematics off for all exps and all rules */ \\
\hspace*{0.5cm} glbSwitchSystematics(GLB\_ALL,GLB\_ALL,GLB\_OFF); \\
\\
\hspace*{0.5cm} /* Calculate Chi2-list as if systematics were on */ \\
\hspace*{0.5cm} double res=CalcSystematics(theldm,thex); \\
\\
\hspace*{0.5cm} /* Switch systematics on for all exps and all rules */ \\
\hspace*{0.5cm} glbSwitchSystematics(GLB\_ALL,GLB\_ALL,GLB\_ON); \\
\\
\hspace*{0.5cm} return res; \\
\} \\
}
\end{quote}

@@

\section{Systematics}

Changing the systematics at running time can be useful to investigate
the impact factors affecting the measurement.
In \GLOBES , the sytematics is defined rule-based, \ie, each rule
has its own systematics. In addition, \AEDL\ requires that it has to be
defined in each rule what ``Systematics on'' and ``Systematics off'' means.
Therefore, it is usually very simple to switch the systematics on and off:
\begin{function}
\GLBNS{glbSwitchSystematics}
{\tt int glbSwitchSystematics(int exp, int rule, int on\_off)}
switches the systematics in experiment {\tt exp} and rule {\tt rule}
on ({\tt on\_off} is \GLB{GLB\_ON}) or off ({\tt on\_off} is \GLB{GLB\_OFF}). For the experiment or
rule index, one can also use \GLB{GLB\_ALL}. 
\end{function}
In the example on page~\pageref{ex:barcharts}, the application of
{\tt glbSwitchSystematics} is demonstrated to show the impact of
systematics, correlations, and degeneracies.

The error dimension (for the definition, see \Sec~\ref{sec:rules}) can also be accessed directly with 
\begin{function}
\GLBNS{glbSetErrorDim}
{\tt int glbSetErrorDim(int exp, int rule, int on\_off, int value)}
sets the error dimension for systematics on ({\tt on\_off} is \GLB{GLB\_ON}) or off ({\tt on\_off} is \GLB{GLB\_OFF}) of experiment {\tt exp} and rule {\tt rule} to the value {\tt value}. The function returns
$-1$ if not successful.
\end{function}
\begin{function}
\GLBNS{glbGetErrorDim}
{\tt int glbGetErrorDim(int exp, int rule, int on\_off)}
returns the error dimension for systematics on ({\tt on\_off} is \GLB{GLB\_ON}) or off ({\tt on\_off} is \GLB{GLB\_OFF}) of experiment {\tt exp} and rule {\tt rule}.
\end{function}

Except from the general treatment of systematics, one can read out
and write the signal and background errors, as well as the background
centers. For the definitions of these quantities, see \Sec~\ref{sec:rules}.
\begin{function}
\GLBNS{glbSetSignalErrors}
{\tt int glbSetSignalErrors(int exp, int rule, double norm, double tilt)}
sets the signal errors of experiment {\tt exp} and rule {\tt rule}
to {\tt norm} (normalization error) and {\tt tilt} (tilt/calibration error).
\end{function}
\begin{function}
\GLBNS{glbGetSignalErrors}
{\tt int glbGetSignalErrors(int exp, int rule, double* norm, double* tilt)}
writes the signal errors of experiment {\tt exp} and rule {\tt rule}
to {\tt norm} (normalization error) and {\tt tilt} (tilt/calibration error).
\end{function}
\begin{function}
\GLBNS{glbSetBGErrors}
{\tt int glbSetBGErrors(int exp, int rule, double norm, double tilt)}
sets the background errors of experiment {\tt exp} and rule {\tt rule}
to {\tt norm} (normalization error) and {\tt tilt} (tilt/calibration error).
\end{function}
\begin{function}
\GLBNS{glbGetBGErrors}
{\tt int glbGetBGErrors(int exp, int rule, double* norm, double* tilt)}
writes the background errors of experiment {\tt exp} and rule {\tt rule}
to {\tt norm} (normalization error) and {\tt tilt} (tilt/calibration error).
\end{function}
\begin{function}
\GLBNS{glbSetBGCenters}
{\tt int glbSetBGCenters(int exp, int rule, double norm, double tilt)}
sets the background centers of experiment {\tt exp} and rule {\tt rule}
to {\tt norm} (normalization center) and {\tt tilt} (tilt/calibrationcenter).
\end{function}
\begin{function}
\GLBNS{glbGetBGCenters}
{\tt int glbGetBGCenters(int exp, int rule, double* norm, double* tilt)}
writes the background centers of experiment {\tt exp} and rule {\tt rule}
to {\tt norm} (normalization center) and {\tt tilt} (tilt/calibration center).
\end{function}
As usual, all these functions return $-1$ if they were not successful.

\section{External parameters in \AEDL\ files}
\label{sec:aedlparams}

@@

\section{Algorithm parameters: Filter functions}

Here come the filter functions
